Bayesian Hierarchical Models for Common Components across Multiple System Configurations

### 2017-08-24 paperDraft2.tex
small edits

\subsection{Assurance Test Planning}
In this section inferences learned from the first three phases of testing will
be used to develop a test plan for the next phase.  Here the objective is to
demonstrate that at a desired level of confidence, the system will meet or
exceed a specified requirement. The methods to be employed will be similar to
the assurance testing as discussed by Hamada et al. ~\cite{ref2}. Bayesian
assurance tests are used to insure that the reliability of an item meets or
exceeds a specified requirement with a desired probability. Although
practitioners often use ``assure'' and ``demonstrate'' synonymously, Meeker and
Escobar ~\cite{ME04} distinguish between reliability demonstration and
reliability assurance testing. A \emph{reliability demonstration test} is
essentially a classical hypothesis test, which uses only the data from the test
to assess whether the reliability-related quantity of interest meets or exceeds
the requirement. A \emph{reliability assurance test}, however, uses
supplementary data and information in order to testing as efficient as possible.

In both classical and Bayesian test planning scenario we are interested in
controlling error rates while minimizing the resources required for testing.  In
the DoD acquisition process the error rates will be referenced in terms of risk.
\emph{Consumer risk} which considers the event of purchasing a product that does
not meet reliability requirements.  \emph{Producer risk} which considers the
event of a product with acceptable reliability failing a given test and not
being considered for purchase.  Introducing the notation for this section, In
the JLTV case study we will be determining how many miles on test $T$, are
required and how many system failures to allow $c$, before the product is
considered unacceptable.  We will define $W(t)$ as a random variable that
represents the total number of system failures after $t$ miles.  Suppose that
$\pi$ denotes some quantity of interest that is related to system reliability at
a given time. It is common to base both classical and Bayesian test plans on two
specified levels of $\pi$: $\pi_0$, an \emph{acceptable reliability level}
(ARL), and $\pi_1$, a \emph{rejectable reliability level} (RRL), where $\pi_1
\leq  \pi_0$. Although the precise definition of ARL and RRL differ between the
classical and Bayesian test criteria, we use them in an equivalent way.

\subsubsection{Classical Approach}
It is quite common to use two criteria in determining classical test plans. The
\emph{producer's risk} is the probability of failing the test when $\pi =
\pi_0$, whereas the \emph{consumer's risk} is the probability of passing the
test when $\pi = \pi_1$.  Suppose that we specify a maximum value, $\alpha$, of
the producer's risk and a maximum value, $\beta$, of the consumer's risk. For
test planning, these criteria become
$$
\begin{aligned}
	\text{Producer's Risk} &= P \text{(Test Is Failed } \vert \pi_0 \text{)} \\ &=
	P \text{(} W(t) > c \vert \pi_0 \text{)} \leq \alpha
\end{aligned}
$$
and
$$
\begin{aligned}
	\text{Consumer's Risk} &= P \text{(Test Is Passed } \vert \pi_1 \text{)} \\ &=
	P \text{(} W(t) \leq c \vert \pi_1 \text{)} \leq \beta
\end{aligned}
$$
To choose a test plan for specified values of $(\alpha, \pi_0, \beta, \pi_1)$,
we assume a distributional form that defines the relationship between the number
of system failyres $W(t)$ and the reliability $\pi$.  Then we can simply find
the combinations of these probabilities by simultaneously solving these two
equations.  In the case where the component failure times are assumed to be
exponentially distributed with rate parameter $\lambda_i$ the failure counts for
each component come from a homogeneous Poisson process $W_i(t) \sim
\text{Poisson}(\lambda_i t)$, and the system failure counts $W(t) \sim
\text{Poisson}(\lambda_S t)$  Numerous textbooks provide additional details of
this purely classical approach.

\subsubsection{Bayesian Approach}
Traditional methods for determining the testing proceedure only rely on
distributional assumptions and/or asymptoic results. With the Bayesian approach
we incorperate the supplementary data from the previous testing phases with the
hopes of minimizing the resorces needed for testing.

@@

>>>>

\subsection{Assurance Test Planning}
In this section we use the resulting reliability model from the previous section
develop a plan for future testing.  Here the objective is to demonstrate that at
a desired level of confidence, the system will meet or exceed a specified
requirement. The methods to be employed will be similar to the assurance testing
as discussed by Hamada et al. ~\cite{ref2}. Bayesian assurance tests are used to
insure that the reliability of an item meets or exceeds a specified requirement
with a desired probability. Although practitioners often use ``assure'' and
``demonstrate'' synonymously, Meeker and Escobar ~\cite{ME04} distinguish
between reliability demonstration and reliability assurance testing. A
\emph{reliability demonstration test} is essentially a classical hypothesis
test, which uses only the data from the test to assess whether the
reliability-related quantity of interest meets or exceeds the requirement. A
\emph{reliability assurance test}, however, uses supplementary data and
information in order to testing as efficient as possible.

In both classical and Bayesian test planning we are interested in controlling
error rates while minimizing the resources required for testing.  In the DoD
acquisition process the error rates will be referenced in terms of risk.
\emph{Consumer risk} which considers the event of purchasing a product that does
not meet reliability requirements.  \emph{Producer risk} which considers the
event of a product with acceptable reliability failing a given test and not
being considered for purchase.  Introducing the notation for this section, In
the JLTV case study we will be determining how many miles on test $T$, are
required and how many system failures to allow $c$, before the product is
considered unacceptable.  We will define $W(t)$ as a random variable that
represents the total number of system failures after $t$ miles.  Suppose that
$\pi$ denotes some quantity of interest that is related to system reliability at
a given time. It is common to base both classical and Bayesian test plans on two
specified levels of $\pi$: $\pi_0$, an \emph{acceptable reliability level}
(ARL), and $\pi_1$, a \emph{rejectable reliability level} (RRL), where $\pi_1
\leq  \pi_0$. Although the precise definition of ARL and RRL differ between the
classical and Bayesian test criteria, we use them in an equivalent way.

\subsubsection{Classical Approach}
It is quite common to use two criteria in determining classical test plans. The
\emph{producer's risk}, defined as the probability of failing the test when $\pi =
\pi_0$, and the \emph{consumer's risk}, defined as the probability of passing
the test when $\pi = \pi_1$.  Suppose that we specify a maximum value, $\alpha$,
of the producer's risk and a maximum value, $\beta$, of the consumer's risk. For
test planning, these criteria become
$$
\begin{aligned}
	\text{Producer's Risk} &= P \text{(Test Is Failed } \vert \pi_0 \text{)} \\ &=
	P \text{(} W(t) > c \vert \pi_0 \text{)} \leq \alpha
\end{aligned}
$$
and
$$
\begin{aligned}
	\text{Consumer's Risk} &= P \text{(Test Is Passed } \vert \pi_1 \text{)} \\ &=
	P \text{(} W(t) \leq c \vert \pi_1 \text{)} \leq \beta
\end{aligned}
$$
To choose a test plan for specified values of $(\alpha, \pi_0, \beta, \pi_1)$,
we assume a distributional form that defines the relationship between the number
of system failyres $W(t)$ and the reliability $\pi$.  Then we can simply find
the combinations of these probabilities by simultaneously solving these two
equations.  In the case where the component failure times are assumed to be
exponentially distributed with rate parameter $\lambda_i$ the failure counts for
each component come from a homogeneous Poisson process $W_i(t) \sim
\text{Poisson}(\lambda_i t)$, and the system failure counts $W(t) \sim
\text{Poisson}(\lambda_S t)$.  Numerous textbooks provide additional details of
this purely classical approach.

\subsubsection{Bayesian Approach}
Traditional methods for determining the testing proceedure only rely on
distributional assumptions and/or asymptoic results. With a Bayesian approach we
incorperate the supplementary data from the previous testing phases with the
hopes of minimizing the resorces needed for testing.

@@

For allowed failures of zero and 1 the math isn't too bad, but when dealing with
systems that  wear down (shape < 1) this will lead to no test plans that will
meet required risk criteria or extreame test plans in terms of resorces.

For more than 1 allowed failure test plans the Weibull computations become
complicated especially for systems with a large number of components.  The one
exception is when a single shape parameter can be assumed accross all compoents.
